Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Extend terminology

\begin{description}
\item[developer]
    A programmer who develops a library.
\item[user]
    A programmer who uses a library.
%%\item[unit test] tests for individual programs or libraries.
\item[example]
    A typical usage example of a function.
\item[property]
    An invariant of a function.
\item[behavior]
    How does a function behave from a users point of view. Behavior can be
    shown by using both examples and properties.
\item[documentation] Explanation of functions.
\end{description}

>>>>

\begin{description}

\item[developer]
    A programmer who develops a library.

\item[user]
    A programmer who uses a library.

\item[example]
    An example shows how a function is used.  It is either a \emph{code
    example} in the form of an HUnit test case; or an \emph{interactive
    example}, given as a short GHCi session.

\item[property]
    Property means a QuickCheck property as defined in~\cite{quickcheck}.

\item[behavior]
    Behavior means an invariant of a function.  We use an informal description
    to refer to a particular behavior, e.g.  "sorts a list" or "launches
    missiles when run".

\item[evidence]
    Evidence is either an example or a property.  It provides some confidence,
    that a function exhibits a certain behavior.

\item[documentation]
    Explanation of functions.
\end{description}
